Comparing distance distributions for top predictive features between bins with and without TADs

### 2019-04-17 Scripts/comparing_distance_densities_by_genomic_bin_class.Rmd
added to results scripts

## Function for ploting distance densities between bins with and without TAD boundaries

```{r}
distplotsfunc <- function(cl, resolution, annotation){
  train <- readRDS(paste0("Z:/TAD_data_analysis/", cl, "/", resolution, "/training_testing/train.rds"))
  data <- train[, c(1, which(names(train)==annotation))]

  set.seed(123)
  majorityids <- sample(x=which(data$y=="No"), size=length(which(data$y=="Yes")))
  annotdata <- rbind.data.frame(data[which(data$y=="Yes"),],
                                data[majorityids,])

@@

  if(perm.pval==0){perm.pval="< 0.0001"}

@@

distplotsfunc(cl="GM12878", resolution="10kb", annotation="Gm12878-08Insulator_dist")

@@

distplotsfunc(cl="GM12878", resolution="25kb", annotation="Gm12878-08Insulator_dist")

@@

distplotsfunc(cl="GM12878", resolution="50kb", annotation="Gm12878-08Insulator_dist")

@@

distplotsfunc(cl="GM12878", resolution="100kb", annotation="Gm12878-08Insulator_dist")

@@

>>>>

## Function for ploting distance densities between bins with and without TAD boundaries from SMOTE resampled data

```{r}
distplotsfunc <- function(cl, resolution, annotation){
  train <- readRDS(paste0("Z:/TAD_data_analysis/", cl, "/", resolution, "/training_testing/train.rds"))

  enetcoefs <- readRDS(paste0("Z:/TAD_data_analysis/", cl, "/", resolution, "/Ensemble/SMOTE/Distance/ENET/enetcoefs.rds"))

  names(train) <- gsub(paste(c("`", 
                             "Gm12878", 
                             "-", 
                             #"_", 
                             #"dist", "count", "perc",
                             "Haib", 
                             "Sydh",
                             "Uta",
                             "Uw",
                             "Broad",
                             "Uchicago"), collapse = "|"), "", names(train))
  train <- train[,c(1,which(names(train) %in% enetcoefs))]

  set.seed(123)
  train_smote <- SMOTE(y ~ ., 
                     data=train, 
                     perc.over = 100, 
                     perc.under = 200)

  annotname <- gsub(paste(c("`", 
             "Gm12878", 
             "-", 
             #"_", 
             #"dist", "count", "perc",
             "Haib", 
             "Sydh",
             "Uta",
             "Uw",
             "Broad",
             "Uchicago"), collapse = "|"), "", annotation)

  #data <- train[, c(1, which(names(train)==annotname))]
  #
  #set.seed(123)
  #majorityids <- sample(x=which(data$y=="No"), size=length(which(data$y=="Yes")))
  #annotdata <- rbind.data.frame(data[which(data$y=="Yes"),],
  #                              data[majorityids,])

  annotdata <- train_smote[, c(1, which(names(train_smote)==annotname))]

@@

  perm.pval <- ifelse(perm.pval==0,"< 0.0001", as.character(round(perm.pval,4)))

@@

#distplotsfunc(cl="GM12878", resolution="10kb", annotation="Gm12878-08Insulator_dist")

@@

#distplotsfunc(cl="GM12878", resolution="25kb", annotation="Gm12878-08Insulator_dist")

@@

#distplotsfunc(cl="GM12878", resolution="50kb", annotation="Gm12878-08Insulator_dist")

@@

#distplotsfunc(cl="GM12878", resolution="100kb", annotation="Gm12878-08Insulator_dist")

@@

# K562

## Function for ploting distance densities between bins with and without TAD boundaries from SMOTE resampled data

```{r}
distplotsfunc <- function(cl, resolution, annotation){
  train <- readRDS(paste0("Z:/TAD_data_analysis/", cl, "/", resolution, "/training_testing/train.rds"))

  enetcoefs <- readRDS(paste0("Z:/TAD_data_analysis/", cl, "/", resolution, "/Ensemble/SMOTE/Distance/ENET/enetcoefs.rds"))

  names(train) <- gsub(paste(c("`", 
                             "K562", 
                             "-", 
                             #"_", 
                             #"dist", "count", "perc",
                             "Haib", 
                             "Sydh",
                             "Uta",
                             "Uw",
                             "Broad",
                             "Uchicago"), collapse = "|"), "", names(train))
  train <- train[,c(1,which(names(train) %in% enetcoefs))]

  set.seed(123)
  train_smote <- SMOTE(y ~ ., 
                     data=train, 
                     perc.over = 100, 
                     perc.under = 200)

  annotname <- gsub(paste(c("`", 
             "K562", 
             "-", 
             #"_", 
             #"dist", "count", "perc",
             "Haib", 
             "Sydh",
             "Uta",
             "Uw",
             "Broad",
             "Uchicago"), collapse = "|"), "", annotation)

  #data <- train[, c(1, which(names(train)==annotname))]
  #
  #set.seed(123)
  #majorityids <- sample(x=which(data$y=="No"), size=length(which(data$y=="Yes")))
  #annotdata <- rbind.data.frame(data[which(data$y=="Yes"),],
  #                              data[majorityids,])

  annotdata <- train_smote[, c(1, which(names(train_smote)==annotname))]

  perm.pval <- ifelse(perm.pval==0,"< 0.0001", as.character(round(perm.pval,4)))

  plottitle <- paste(gsub(paste(c("K562",
                                  "-","_",
                                  "dist","perc","count",
                                  "Haib",
                                  "Sydh",
                                  "Uta",
                                  "Uw",
                                  "Broad",
                                  "Uchicago"), 
                                collapse = "|"), 
                          "",
                          annotation))

distplotsfunc(cl="K562", resolution="10kb", annotation="K562-Ctcf-Broad_dist")

distplotsfunc(cl="K562", resolution="10kb", annotation="K562-Smc3ab9263-Sydh_dist")

distplotsfunc(cl="K562", resolution="10kb", annotation="K562-Znf143166181ap-Sydh_dist")

distplotsfunc(cl="K562", resolution="10kb", annotation="K562-Rad21-Haib_dist")

#distplotsfunc(cl="K562", resolution="10kb", annotation="K562-08Insulator_dist")

distplotsfunc(cl="K562", resolution="10kb", annotation="K562-Yy1sc281-Haib_dist")

distplotsfunc(cl="K562", resolution="10kb", annotation="K562-DNase_dist")
```

distplotsfunc(cl="K562", resolution="25kb", annotation="K562-Ctcf-Broad_dist")

distplotsfunc(cl="K562", resolution="25kb", annotation="K562-Smc3ab9263-Sydh_dist")

distplotsfunc(cl="K562", resolution="25kb", annotation="K562-Znf143166181ap-Sydh_dist")

distplotsfunc(cl="K562", resolution="25kb", annotation="K562-Rad21-Haib_dist")

#distplotsfunc(cl="K562", resolution="25kb", annotation="K562-08Insulator_dist")

distplotsfunc(cl="K562", resolution="25kb", annotation="K562-Yy1sc281-Haib_dist")

distplotsfunc(cl="K562", resolution="25kb", annotation="K562-DNase_dist")
```

distplotsfunc(cl="K562", resolution="50kb", annotation="K562-Ctcf-Broad_dist")

distplotsfunc(cl="K562", resolution="50kb", annotation="K562-Smc3ab9263-Sydh_dist")

distplotsfunc(cl="K562", resolution="50kb", annotation="K562-Znf143166181ap-Sydh_dist")

distplotsfunc(cl="K562", resolution="50kb", annotation="K562-Rad21-Haib_dist")

#distplotsfunc(cl="K562", resolution="50kb", annotation="K562-08Insulator_dist")

distplotsfunc(cl="K562", resolution="50kb", annotation="K562-Yy1sc281-Haib_dist")

distplotsfunc(cl="K562", resolution="50kb", annotation="K562-DNase_dist")
```

distplotsfunc(cl="K562", resolution="100kb", annotation="K562-Ctcf-Broad_dist")

distplotsfunc(cl="K562", resolution="100kb", annotation="K562-Smc3ab9263-Sydh_dist")

distplotsfunc(cl="K562", resolution="100kb", annotation="K562-Znf143166181ap-Sydh_dist")

distplotsfunc(cl="K562", resolution="100kb", annotation="K562-Rad21-Haib_dist")

#distplotsfunc(cl="K562", resolution="100kb", annotation="K562-08Insulator_dist")

distplotsfunc(cl="K562", resolution="100kb", annotation="K562-Yy1sc281-Haib_dist")

distplotsfunc(cl="K562", resolution="100kb", annotation="K562-DNase_dist")
```
